Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Remove IEEE author block.
Have to redo it.
Remove grammar notes that are making me crazy.

% ANON
% \author{David Fifield, Chang Lan}
% \author{
% \IEEEauthorblockN{David Fifield and Chang Lan}
% \IEEEauthorblockA{University of California, Berkeley}
% }

@@

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
\vp{Try not to begin sentences with ``Then'' (or with conjunctions like
``But'').  Also, the writing has a lot of passive voice here.}
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

@@

\vp{Lots of passive in this paragraph}
Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that reside
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it does not require active cooperation by network intermediaries.

>>>>

@@

To the above challenges we add a related one, active probing.
An active-probing censor does not merely passively observe traffic:
it injects its own traffic,
acting as if it were an ordinary client and connecting to suspected
proxy servers to see how they respond.
Then a connection is successful, the server can be blacklisted.
Active probing is a precise means of identifying whether a server belongs to a circumvention system,
even when a protocol is hard to detect on the wire.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing scans that follow up on observed client connections, to discover
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and obfs4~\cite{obfs4},
described in this section.

@@

Decoy routing~\cite{decoyrouting}
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
For this reason, it is also called end-to-middle proxying.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
Decoy routing asks friendly ISPs to deploy special routers that reside
on network paths between censored users and uncensored ``decoy'' Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by the special routers, and not by the censor.
On receiving a tagged communication, the router shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar in spirit to decoy routing:
think of domain fronting as decoy routing at the application layer.
In place of a router, domain fronting has a frontend server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while fronting uses the HTTP Host header, encrypted within HTTPS.
Fronting has the advantage that it does not require active cooperation by network intermediaries.
